A formal approach but practical approach in train regulation

### 2025-06-19 paper/main.tex
Unification direction

We suppose that the train network can be described as follows. First, we consider given a set of blocks: $\blocks = \{ 1, 2, \ldots, n\}$. Blocks are oriented: there is a $\forward$ end and a $\backward$ one. Let $\directions = \{\forward, \backward\}$ be the two directions.  Next, we suppose given a set $\turnouts = \{ n+1, \ldots, m\}$, the identifiers  of trackworks (switches, crossings, double slip switches, and so on\todo{Est-ce que ces élements sont dans le modèle de Lucas, en particulier les crossings et double slip switches ?}). Trackworks are characterized by an internal state: switches can be in direct or deviate position (next denoted '\direct' and '\deviate'), a crossing has only one internal position, a double slip switch can be straight through or crossing. In the examples, to simplify the presentation, we use only switches, but our model is not restricted to them.  Let $\internalState$ denotes the set of internal states. A \emph{network configuration} is given by a function $\sigma: \turnouts \to \internalState$. Let $\networkConf$ denotes the set of all network configurations. For two turnouts $\theta = \{9, 10\}$, the function $9 \mapsto \deviate, 10 \mapsto \direct$ states that $9$ is in deviate position while 10 is in direct one. The latter function is also described via an array  $[\deviate, \direct]$ giving states in trackwork order.

@@

\subsection{Agents}
\paragraph{Trains.}
We now present the train model.
Each train is characterised by an identifier, a position, a direction, and a list of orders.
\begin{itemize}
	\item Train identifiers form a set  $\trains = \{1, \ldots, k\}$.
	\item The position is the index of the block currently occupied by the train.
	\item The direction direction in $\directions = \{\dirBackward, \dirForward, \dirStop\}$ --- where \dirBackward (resp.\ \dirForward) indicates the trains is ordered to go towards the \backward (resp.\ \forward) end of the block, while \dirStop indicates the train has no direction order at the moment. The direction represent the current move order, but does not mean the train is actually moving: it can be blocked at a signal.
	\item Orders are given as a (possibly empty) sequence of orders $\su{dir}{pos}$ ($\dirFmt{dir} \in \directions$, $\posFmt{pos} \in \blocks$). Such order states that the train direction is set to $\dirFmt{dir}$ and that the train runs until it reaches $pos$.
\end{itemize}

>>>>

We suppose that the train network can be described as follows. First, we consider given a set of blocks: $\blocks = \{ 1, 2, \ldots, n\}$. Blocks are oriented: there is a $\dirForward$ end and a $\dirBackward$ one. Let $\directions = \{\dirForward, \dirBackward\}$ be the set of directions.  Next, we suppose given a set $\turnouts = \{ n+1, \ldots, m\}$, the identifiers  of trackworks (switches, crossings, double slip switches, and so on\todo{Est-ce que ces élements sont dans le modèle de Lucas, en particulier les crossings et double slip switches ?}). Trackworks are characterized by an internal state: switches can be in direct or deviate position (next denoted '\direct' and '\deviate'), a crossing has only one internal position, a double slip switch can be straight through or crossing. In the examples, to simplify the presentation, we use only switches, but our model is not restricted to them.  Let $\internalState$ denotes the set of internal states. A \emph{network configuration} is given by a function $\sigma: \turnouts \to \internalState$. Let $\networkConf$ denotes the set of all network configurations. For two turnouts $\theta = \{9, 10\}$, the function $9 \mapsto \deviate, 10 \mapsto \direct$ states that $9$ is in deviate position while 10 is in direct one. The latter function is also described via an array  $[\deviate, \direct]$ giving states in trackwork order.

@@

\subsection{Agents}
\paragraph{Trains.}
We now present the train model.
Each train is characterised by an identifier, a position, a direction, and a list of orders.
\begin{itemize}
	\item Train identifiers form a set  $\trains = \{1, \ldots, k\}$.
	\item The position is the index of the block currently occupied by the train.
	\item The direction (taken from $\directions_\dirStop = \{\dirBackward, \dirForward, \dirStop\}$) indicates the direction the train is ordered to go towards, where \dirStop indicates the train has no direction order at the moment. The direction represent the current move order, but does not mean the train is actually moving: it can be blocked at a signal.
	\item Orders are given as a (possibly empty) sequence of orders $\su{dir}{pos}$ ($\dirFmt{dir} \in \directions$, $\posFmt{pos} \in \blocks$). Such order states that the train direction is set to $\dirFmt{dir}$ and that the train runs until it reaches $pos$.
\end{itemize}
